\documentclass[letterpaper,11pt]{article}
\include{preamble}
\usepackage{latexsym}
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Charles Shaw} \\ \vspace{15pt}
\small 
\hspace{1pt} \faEnvelope \hspace{1pt} \texttt{charles@charlesshaw.net} \hspace{1pt} $|$
\hspace{1pt} \faMapMarker* \hspace{1pt}\texttt{London, UK}  \hspace{1pt} $|$
\hspace{1pt} \faGithub \hspace{1pt} \texttt{github.com/shawcharles} \hspace{1pt} $|$
\hspace{1pt} \faPhone \hspace{1pt} \texttt{+44 (0) 7955 229 370} \hspace{1pt}
%\\ \vspace{-3pt}
\end{center}

%-----------PROFILE-----------
\section{PROFILE}

\begin{itemize}
\item Econometrician / Data Scientist with experience working in media and finance, and expertise in statistical modelling for descriptive, predictive, and causal inference, as well as data science techniques.
\item Interested in jobs focusing on econometric modelling, possibly on the intersection of economics / marketing and data science. London or fully remote preferred, but will consider relocating for the right opportunity. 

\end{itemize}
%\\ \vspace{-3pt}
     
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{T\&Pm (www.tandpgroup.com)}{March '24 - present}
{Data Science Director}{London, UK}
\resumeItemListStart
\resumeItem{The merger of two WPP agencies, GroupM media shop mSix and creative agency network The\&Partnership created both the UK's largest and Europe's fastest-growing independent agency network.}
\resumeItem{Collaborating closely with key stakeholders in the media sector, including C-suite executives, to provide data-backed recommendations that drive transformative impact.} 
\resumeItem{Responsible for discovery, development and delivery of analytics products.}
\resumeItem{Delivered analyst training (UK and US offices).}
\resumeItemListEnd


\resumeSubheading
{mSix\&Partners (www.msixandpartners.com)}{March '22 - March '24}
{Data Science Director}{London, UK}
\resumeItemListStart
\resumeItem{mSix\&Partners is a media, commerce and content agency with 1500 people across 49 offices globally.}
\resumeItem{Invited speaker at industry conferences, speaking on causal inference and other such matters.}
\resumeItem{Clients include Electronic Arts, Amazon, Toyota, and others.}
\resumeItem{Accomplishments: }
\begin{itemize}
\item Built analytics libraries for MMM, marketing econometrics and media effectiveness measurement.
\item Focusing on data-driven commercial approaches, identifying opportunities to maximize revenue.

\end{itemize}

\resumeItem{Awards: }
\begin{itemize}
\item 2023 MediaTel Awards Best Agency Research Project.
\item 2023 Mediaweek Awards -- my work for National Express was shortlisted for Best Use of Econometrics ("A new multidimensional approach to MMM econometrics")
\end{itemize}
\resumeItemListEnd

\resumeSubheading
{FixedPoint IO Ltd. (www.fixedpoint.io)}{Jan '2021 - present}
{Director}{London, UK}
\resumeItemListStart
\resumeItem{Boutique data consulting firm specializing in econometric modelling and data analysis}
\resumeItem{Work done for various industries incl. media, asset management (US-based hedge fund), finance (insurance), advisory (carbon trading) and others.}
\resumeItemListEnd

\resumeSubheading
{Ocean Media Group Ltd. (www.oceanmedia.co.uk)}{Aug '16 - July '21}
{Head of Data \& Audience Development}{London and Manchester, UK}
\resumeItemListStart
\resumeItem{Ocean Media Group's range of services includes trade magazine and newspaper publishing, event and conference organisation, market research and measurement, news distribution, and on-line information products. I had a dual role, where:}

\resumeItem{First, I oversaw portfolio data and systems incl. benchmarks, metrics, and best practices to ensure long term audience growth. Built analytics solutions that covered editorial content, audience/persona creation, and subscription data to enable stakeholders to visualise, analyse \& assess effectiveness of their marketing/content strategies.}
\resumeItem{Second, I was also directly responsible for \pounds 2.4m of revenue. I managed a team of 4  and looked after audience revenue for 14 products (conferences, exhibitions, awards). Additional responsibility for BI, integration across data sources/systems, database capabilities, insight, shadow IT across a diverse estate of systems, GDPR/DPA/PECR, data quality, reporting, implementing quality assurance controls, and analytics.}

\resumeItem{Accomplishments: }
\begin{itemize}
\item Delivered growth in conference business from \pounds 1.1m to \pounds 2.4m.
\item Repositioned a historically underperforming awards business, reversing falling revenues, and moving to growth within one financial year.
\item Hired, developed, and managed a team of 4. Conducted regular internal training \& development to improve statistical literacy within the business. 
\item Built data pipelines to automate reporting of key data while incorporating various APIs \& libraries. Served as a tech lead on all assigned projects, including all BI, ETL, and related matters. 
\end{itemize}
\resumeItem{Awards: }
\begin{itemize}
\item Awards Awards 2018, best awards event by a publisher
\item Association of Event Organisers Awards 2020, best conference
\item Bronze, GCN Global Conference Awards 2018, UK conference of the Year
\item Bronze, Awards Awards 2018, Housing Heroes, best awards event alongside a conference
\item Silver, Awards Awards 2018, UK Housing Awards, best long standing awards event
\end{itemize}
\resumeItemListEnd
%\resumeSubHeadingListEnd

%\resumeSubHeadingListStart
\resumeSubheading
{Minerva Statistical Consulting Ltd}{Aug '16 - Sep '18}
{Economic Adviser}{London, UK}
\resumeItemListStart
\resumeItem{Supporting delivery of economic analysis, assisting senior economists and decision makers.}
\resumeItem{Advised on various econometric projects, including energy demand modelling, and commodity market analysis.}
\resumeItemListEnd
%\resumeSubHeadingListEnd

%\resumeSubHeadingListStart
\resumeSubheading
{RELX Group PLC}{Sep '15 - '16}
{Analyst, Team Leader}{London, UK}
\resumeItemListStart
\resumeItem{RELX is a global provider of information-based analytics for professional and business customers across industries.}
\resumeItem{Managing 2 direct reports, I supported the data function and provided BI-focused solutions.}
\resumeItemListEnd
%\resumeSubHeadingListEnd

%\resumeSubHeadingListStart
\resumeSubheading
{Analyst (Contract)}{Jun '15 - Sep '15}
{AIP}{London, UK}
\resumeItemListStart
\resumeItem{AIP is a financial advisory firm focused on Commodities and Artificial Intelligence.}
\resumeItem{Provided analysis of opportunities across energy, commodities, and mining.}
\resumeItemListEnd
%\resumeSubHeadingListEnd

%\resumeSubHeadingListStart
\resumeSubheading
{Researcher}{Sep '13 - Jun '15}
{Companies \& Markets}{London, UK}
\resumeItemListStart
\resumeItem{Coverage of global industrial and commodity markets.}
\resumeItemListEnd
%\resumeSubHeadingListEnd

%\resumeSubHeadingListStart
\resumeSubheading
{Senior Business Analyst}{Oct '11 - Sep '13}
{Groupe PSA}{London and Coventry, UK}
\resumeItemListStart
\resumeItem{Managed the technical relationship for a EUR 74bn European automotive multinational, focusing on wholesale strategy and increasing market share of Group products and solutions.}
\resumeItem{Provided data analytics, SQL/DBMS support, applied appropriate database management processes and modelling techniques.}
%Achievements: Helped increase market share for fleet product by 14\% in two years, despite the fact that the Group was strongly exposed to the mature European market, in a context of relative saturation of vehicle fleets and reduced space allocated for vehicles in urban areas. 
\resumeItemListEnd
%\resumeSubHeadingListEnd

%\resumeSubHeadingListStart
\resumeSubheading
{Previous roles}{}{Various roles, not necessarily related to my current interests}{}
\resumeItemListStart
\resumeItem{Including Commodity Finance at Deutsche Bank, and others.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------CERTS-----------
\section{CERTIFICATIONS}
 \begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{~} { Council of Europe Certificate in Data Protection \& Privacy Rights }\vspace{2pt} \\
\textbf{~} { IBM Data Engineering Professional Certificate} \vspace{2pt} \\
\textbf{~} { European Information Technologies Certification Programme - EITCA Artificial Intelligence Academy}   
    }}
 \end{itemize}
 

%-----------AWARDS-----------
\section{AWARDS}
 \begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Institute of Economic Affairs (IEA)} {: IEA Richard Koch Breakthrough Prize, Highly Commended. Prize money: \pounds 2,500.} \vspace{2pt} \\
\textbf{PRMIA}     {: European Finalist, PRMIA Risk Management Challenge 2017. I led a three-man team that reached European final. Led on the development and MATLAB implementation of a Bayesian MCMC market risk model to stress test financial scenarios. The PRMIA Risk Management Challenge is hosted in Europe and North America by the Professional Risk Managers' International Association.} \vspace{2pt} \\
%\textbf{Projects}  {: Dryad, an automated Marketing Mix Modeling (MMM) library (Python, proprietary)}
}}
 \end{itemize}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
{University of Strathclyde}{~}
{MSc Applied Statistics }{Glasgow, UK}
\begin{itemize}
\item[] 
\end{itemize}

\resumeSubheading
{University of London, Birkbeck College}{~}
{MSc Financial Mathematics}{London, UK}
\begin{itemize}
\item[] Thesis: Three Essays on Nonlinear Time-series Econometrics. Thesis marked as exemplary (86\%), with one chapter published in \textit{Journal of Statistics: Advances in Theory and Applications} (vol. 20:1, pp15-65). 
\end{itemize}

\resumeSubheading
{University of London, Birkbeck College}{~}
{BSc(Econ) Financial Economics}{London, UK}
\begin{itemize}
\item[] 1st XV Rugby. 2x BUCS London Champions, 1x Middlesex Sevens Universities Cup. Cricket Club Secretary. Full Colour (the only Full Colour awarded that year). Thesis marked as exemplary and distributed to subsequent years as a top example.
\end{itemize}
\resumeSubHeadingListEnd

%-----------PEER REVIEWED PUBLICATIONS-----------
\section{PEER REVIEWED PUBLICATIONS}
 \begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Shaw C.}, Vanadia, S. (2022) "Utilitarianism on the front lines: COVID-19, public ethics, and the 'hidden assumption' problem" \textit{Ethics \& Bioethics (12(1-2), pp.60-78)} \\
\textbf{Shaw C.}, (2022) "Dynamic causal effects of pandemic-induced uncertainty on output, credit, and asset prices: a Symbolic Transfer Entropy approach". \textit{Industrial Engineering \& Management Systems} (vol 21:1, pp119-127)\\
\textbf{Shaw C.}, (2018) "Conditional Heteroskedasticity in Cryptoasset Returns". \textit{Journal of Statistics: Advances in Theory and Applications} (vol. 20:1, pp15-65) \\
\textbf{Shaw C.}, Pycock, D. (2019). "Simplified Planning Zones and the realignment of fiscal incentives", \\
in \textit{Raising the Roof: How to Solve the United Kingdom's Housing Crisis} (published by: Institute of Economic Affairs)
    
    }}
 \end{itemize}

\section{SELECTED MEDIA REFERENCES}
 \begin{itemize}[leftmargin=0in, label={}]
\small{\item{ 
\textbf{Shaw C.}, Pycock, D., \href{https://capx.co/more-homes-lower-prices-the-case-for-simplified-planning-zones/}{More homes, lower prices: the case for Simplified Planning Zones.} CapX / Policy Exchange, Oct 2018 \vspace{2pt} \\
 \textbf{Shaw C.}, Pycock, D., \href{https://iea.org.uk/untangling-the-complex-web-of-the-uk-housing-market/}{Untangling the complex web of the UK housing market.} Institute of Economic Affairs, Oct 2018 
    }}
 \end{itemize}

 %-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Computing: } {Python, R, MATLAB, Stata, PowerBI, and various frameworks / libraries.}\vspace{2pt} \\
\textbf{Methodologies: } {Time-series and panel data econometrics, causal inference techniques, frequentist and Bayesian statistics, clustering methods, constrained optimisation.}\vspace{2pt} \\

    }}
 \end{itemize}

  %----------PERSONAL-----------
\section{PERSONAL}
 \begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Rugby} {: Phantoms RFC, Wanstead RFC, Birkbeck 1st XV RFC. Achievements: twice Winner of British Universities' London Division 1 Rugby Title, Middlesex Sevens Mens' Universities Cup, Essex Division 6 Shield.}\vspace{2pt} \\
\textbf{Citizenship}     {: United Kingdom} \\    
\textbf{Languages}     {: English (native), Russian (fluent), German (rusty).} \\  
    }}
 \end{itemize} 

\footnotesize
\vfill
Last modified \today
\end{document}
